---
output: github_document
editor_options: 
  chunk_output_type: console
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# osgeo.gdal

<!-- badges: start -->
<!-- badges: end -->

The goal of osgeo.gdal is to get access to the Python gdal package.  It's helping me learn how it works and how GDAL itself works. 

## Installation

You can install the development version of osgeo.gdal like so:

``` r
# FILL THIS IN! HOW CAN PEOPLE INSTALL YOUR DEV PACKAGE?
```

## Example

Very silly example for now, we just have a geometry reader and it can be reprojected to a local crs. 

Can turn on the reprojection, can turn on simplification (try reading just one at a time, it's about 200Mb of geometry total over a url). 


```{r example}
library(osgeo.gdal)
## basic example code
plot(og_read_geometry(ia = 50))
plot(og_read_geometry(ia = 50, simplify = 1))
plot(og_read_geometry(ia = 50, simplify = .1))

## to get the feature's fields use same index
og_read_fields(ia = 50)

og_read_fields(ia = 60:62)

allfields <- og_read_fields(ia = 1:200)

idx <- match(c("CAN", "MEX", "USA"), allfields$shapeGroup)
plot(og_read_geometry(ia = idx, simplify = .05))


## finally, apply the local custom projection
plot(og_read_geometry(ia = idx[1], simplify = .05, localproject = TRUE))

plot(og_read_geometry(ia = which(allfields$shapeGroup == "ATA"), simplify = .05, localproject = TRUE))

```


## Code of Conduct
  
Please note that the osgeo.gdal project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/1/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
